TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-01 paper/paper.tex
Added sections for results

	In both scenarios the TCP congestion algorithms are tested for multiple characteristics:
	\begin{enumerate}
		\item TCP Window Size measured over time: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of a larger window or a smaller window to a specific TCP connection.
		\item Bandwidth allocation: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more bandwidth to a specific TCP connection.
		\item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.
	\end{enumerate}
The tests conducted on the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. Packet loss and delay are chosen as the behavior of most TCP algorithms depend on those variables. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.

@@

@@

\section{Results}

>>>>

	In both scenarios the TCP congestion algorithms are tested for multiple characteristics:
	\begin{enumerate}
		\item TCP Window Size measured over time: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of a larger window or a smaller window to a specific TCP connection.
		\item Bandwidth allocation: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more bandwidth to a specific TCP connection.
		\item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.
	\end{enumerate}
The tests conducted on the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. Packet loss and delay are chosen as the behavior of most TCP algorithms depend on those variables [SRC]. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.

@@

		\subsubsection{Testing hardware}
		The specifications of the hardware used for the tests are shown in table \ref{table:spec1}, table \ref{table:spec2} and table \ref{table:spec3}. The switch shown in table \ref{table:spec3} has all router related functionalities, which might impact the network speed, turned off.

		\begin{table}[H]
			\centering
			\caption{Node configurations}
			\begin{tabular}[H]{ | l | l | }
			\hline
			\textbf{Hardware} & \textbf{Specification} \\
			\hline  Model & Dell Optiplex 7010\\
			\hline  CPU & Intel(R) Core(TM) i5-3570S CPU @ 3.10GHz\\
			\hline  Memory & 12GB\\
			\hline  NIC & Intel Corporation 82579LM Gigabit Network Connection (rev 04)\\
			\hline	NIC Driver & e100e 3.2.6-k\\
			\hline
			\end{tabular}
			\label{table:spec1}
		\end{table}

		\begin{table}[H]
			\centering
			\caption{Switch 1 configuration}
			\begin{tabular}[H]{ | l | l | }
			\hline
			\textbf{Hardware} & \textbf{Specification} \\
			\hline  Model & 3Com OfficeConnect Gigabit Switch 16\\
			\hline  Ports & 16x Gigabit Ethernet\\
			\hline
			\end{tabular}
			\label{table:spec2}
		\end{table}

		\begin{table}[H]
			\centering
			\caption{Switch 2 configuration}
			\begin{tabular}[H]{ | l | l | }
			\hline
			\textbf{Hardware} & \textbf{Specification} \\
			\hline  Model & Sitecom Gigabit Router 300N-XR\\
			\hline  Ports & 4x Gigabit Ethernet\\
			\hline
			\end{tabular}
			\label{table:spec3}
		\end{table}

@@

\section{Results}
	\subsection{TCP Congestion Algorithms}
	The most common TCP congestion algorithms are CTCP, CUBIC and BIC. CTCP is the default congestion algorithm in Microsoft Windows Server Editions and Microsoft Windows 8 and newer [SRC]. CUBIC is the default congestion algorithm in Linux distributions with kernel versions ... and newer [SRC]. BIC was the default congestion algorithm in earlier Linux distributions with kernel versions: [SRC]. DCTCP and BBR will also be tested as those protocols are newer. DCTCP is specifically designed for datacenters [SRC] and BBR is a new congestion protocol not yet widely deployed [SRC].

		\subsubsection{Algorithm Characteristics}
		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).

		\subsubsection{Performance comparison}	
		- Includes results of tests.

	\subsection{Traffic Management}
	- Includes what is available for trafic management in a datacenter.
	- Measures to take to equally allocate bandwidth to customers.
		\subsubsection{Quality of Service}
